%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace*{0.01}
\namesection{Rajath}{John Bosco}
{ 
\href{mailto:rajathj2@illinois.edu}{rajathj2@illinois.edu} | +1-(217)-819-8905
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Illinois at Urbana-Champaign}
\descript{MS in Information Management (Data Science Track )}
\location{Exp. Grad May 2021| Champaign, IL  \\}
\sectionsep
\vspace{5pt}
\subsection{SJCE (JSSST University)}
\descript{BE in Computer Science}
\location{Grad July 2016 | Mysore, India  \\ Cum. GPA: 8.5}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{MOOC}
Machine Learning-Coursera \\
Deep Learning Specialisation - Coursera* \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Data Structures\\
Design and Analysis of Algorithms \\ 
Big Data Analytics \\
Software Engineering \\
Operating Systems \\
Computer Networks\\
Probability Statistics and Queuing\\
Finite Automata and Formal Languages \\
Computer Graphics\\ 
Database Management and Systems \\ 
Advanced Web Technologies \\
Advanced Computer Architecture\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\location{Programming :}
Java \textbullet{}  Python \textbullet{} C  \\ 
\location{Web Programming :}
HTML \textbullet{} CSS \textbullet{} Javascript  \\
\location{Familiar:}
Tableau \textbullet{}TensorFlow  \textbullet{} Hadoop
\textbullet{}Hbase
\textbullet{}Spark
\textbullet{}Kafka
\textbullet{}Hive
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Volunteering Exp.}
\location{Visa Hackathon}
\textbullet{}Volunteered in Editing and Tech Infrastructure teams during the events. \linebreak 
\location{Java Tutor - Computer Paradise}
\textbullet{}I volunteered as a Java tutor to a foreign international for three months. \linebreak
\location{Visa CSR} 
\textbullet{}Volunteered many events like helping physically challenged students, Oxfam Trailwalker, Charity visits etc. \linebreak 
\location{Helping Hands}  
\textbullet{}Helped poor students, people by raising funds, holding meetups etc.


\sectionsep


\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Visa Inc | Operations and Infrastructure \newline}
%%\descript{}
\location{Systems Analyst | December 2018 - August 2019 | Bangalore, India \newline
}
\begin{tightemize}
\item \ Worked on Visa Artificial Intelligence Platform (VAIP)\texttrademark, Tokenization (Apple Pay\texttrademark, Google Pay\texttrademark, Android Pay\texttrademark, Samsung Pay\texttrademark, NetFlix Pay\texttrademark, Fitbit Pay\texttrademark etc) and Verified by Visa (VBV)\texttrademark. 
\item Developed scripts for checking vital processes,overall system heath-check , kernel details and worked on CI/CD pipeline to  deploy them in real-time for VAIP. 
\item  Reduced 75\% of the overall time involved in the remediation of the servers by deploying shell scripts to start and stop instances for VBV and Tokenization.
\item  Received 19 “Go Beyond” - Corporate recognition for handling important releases, issues and for volunteering in Hackathon, Rio Olympics’ Promotion and charity events.
\end{tightemize}
\location{Associate Systems Analyst | July 2016 – December 2018| Bangalore, India
}
\begin{tightemize}
\item  Successfully on-boarded 39 banks across the world for Tokenization by validating API calls,SSL certificates and providing key suggestions to improve QoS.
\item Designed Dashboards, visualized transaction data with the help of Splunk to calculate metrics and monitor applications in real-time for VBV, VAIP and Tokenization.
\item  Automated the process of checking connectivity between application and remote servers by enabling passwordless-SSH through Shell scripts in a multi-tier architecture, effectively reducing the time by 50\%.
\end{tightemize}


\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Product Analysis in Social Media using Data Analytics}

\begin{tightemize}


\item \normalsize {Worked on Information Retrieval techniques to develop a generic platform to visualize and compare specifications of products.
\item Achieved 82\% accuracy through sentiment analysis by using NLTK on product reviews obtained through Social Media (Facebook, Twitter) in Real-time.} \end{tightemize}
\sectionsep

\runsubsection{Prediction of Diabetes }
\begin{tightemize}
\item \normalsize { Achieved 90\%  accuracy while predicting diabetes using Pima Indians Diabetes Data-set with the help of ML algorithms like Logistic Regression and KNN.} \end{tightemize}
\sectionsep

\runsubsection{Credit Card Fraud Detection }
\begin{tightemize}
\item \normalsize {Achieved 86\% accuracy while classifying credit card frauds with the help of Sampling and logistic regression on an imbalanced Data-set} \end{tightemize}
\sectionsep


\runsubsection{Merchant Locator Chatbot }
\begin{tightemize}
\item \normalsize {Built a chatbot to find the nearest Merchant who is available in a disaster affected area with the help of POS ( Point of Sale)  data}\end{tightemize}
\sectionsep

\runsubsection{Gold Price Prediction System}
\begin{tightemize}
\item \normalsize {Predict the increase or decrease in gold prices, based on inter-market variables, using Logistic Regression and SVM.}
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Activities }


\runsubsection{Linux Campus Club SJCE \vspace{.5mm}}
\descript{| Executive Committee }
\begin{tightemize}
\item \normalsize {Conducted Sessions on Python , GIT , Machine Learning and worked on installing Ubuntu OS, Open Source Software on all the laboratory Systems.}
\item \normalsize {Promoted Linux to over 600 active members in the campus by conducted quizzes, programming competitions as part of the annual fests -FOSSCAMP & FOSSBYTE.}
\end{tightemize}
\sectionsep

\runsubsection{Student Council SJCE \vspace{1mm} }
\descript{| Editor, SMM, Host ( 2015, 2016 ) }

\begin{tightemize} 
\item \normalsize {Communicated and gave presentations to potential sponsors for the annual fest Jayciana, which helped in garnering funds of 15,000\$.} \\

\end{tightemize}
\sectionsep

%%%
%\runsubsection{Visa Skunkworks}
%\begin{tightemize}
%\item \normalsize {Currently Working on Ops-Chatbot to proactively monitor Servers.}\\
%%%

%\end{tightemize}

\sectionsep



\end{minipage} 
\end{document}